---
title: "HW3_sliang"
author: "Liang Shi"
date: "9/26/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(vioplot)
library(ggplot2)
```

# Problem 3

I'm familiar with almost of these rules. What impress me is the rule "Don't use attach()". So I make some research and find out if we have several different datasets, the cold will become messy.

# Problem 5

```{r}
df <- readRDS("HW3_data.rds")

get_result <- function(df){
  mean_1 <- mean(df$dev1)
  mean_2 <- mean(df$dev2)
  sd_1 <- sd(df$dev1)
  sd_2 <- sd(df$dev2)
  corr_12 <- cor(df$dev1, df$dev2)
  return (c(mean_1, mean_2, sd_1, sd_2, corr_12))
}

df_organized <- data.frame(Observer = NULL, Mean_1 = NULL, Mean_2 = NULL, SD_1 = NULL, SD_2 = NULL, Corr_12 = NULL)

for (i in 1:13){
  result <- get_result(df[df$Observer == i, 2:3])
  df_cur_observer = data.frame(Observer = i, Mean_1 = result[1], Mean_2 = result[2], SD_1 = result[3], SD_2 = result[4], Corr_12 = result[5])
  df_organized <- rbind(df_organized, df_cur_observer)
}
kable(df_organized)
```

```{r}
boxplot(df$dev1, main = "Dev1")
boxplot(df$dev2, main = "Dev2")
```

These two distribution are almost symmertic, and no outliers here.

```{r}
vioplot(df$dev1, main = "Dev1")
vioplot(df$dev2, main = "Dev2")
```

From the vioplot, we know that in dev1, the mode is near the median, but in dev2, the mode is a little skew from the median. And we can also see that the standard deviation of dev2 is larger than of dev1.

```{r}
ggplot(df, aes(x=dev1,y=dev2)) + geom_point() + facet_wrap(Observer~.)
```

I see many funny plots. From the scatter plot, we know the correlation between dev1 and dev2 is very weak, which agree with our data summary. I think plot the data is a very important way before analysis, because statistics only may misleading our approach.

# Problem 6

```{r}
get_integral <- function(x){
  y <- exp(- (x^2 / 2))
  return(y)
}

x_range <- seq(0, 1, by = 1e-6)
sum(get_integral(x_range) * 1e-6)
```

# Problem 7

```{r}
fx <- function(x){
  y <- 3^x - sin(x) + cos(5*x)
}

fdx <- function(x){
  y <- 3^x*log(3) - cos(x) - 5*sin(5*x)
}

ggplot(data = data.frame(x = 0,y = 0), mapping = aes(x = x)) + 
  stat_function(fun = fx) + 
  xlim(-5, 2.5) + 
  geom_abline(intercept = 0, slope = 0, colour = "red")

x <- -2.5
while (abs(fx(x)-0) > 1e-6) {
  x <- x - fx(x)/fdx(x)
}
x
```

# Problem 8

```{r}
start <- Sys.time()
X <- cbind(rep(1,100),rep.int(1:10,time=10))
beta <- c(4,5)
y <- X%*%beta + rnorm(100)
I <- diag(100)
NJ_1 <- rep(1/100, 100)
y_A <- vector()
for (i in 1:100){
  a <- I[,i] - NJ_1
  num <- t(y)%*%a
  y_A[i] <- num
}
SST = t(y_A)%*%y
print(SST)
end <- Sys.time()
print(end - start)
```